---
title: "Assignment3"
author: "Manying"
date: "19/11/2017"
output: html_document
---

```{r}
source("functions.R")
```

## Exercise 1

```{r}
`%>%` <- magrittr::`%>%`
```

### Task A

```{r}
d <- stressshift::stress_shift_unamb
print(d)
stress_shift_3dict <- dplyr::filter(d,Dict=="W1802"|Dict=="J1917"|Dict=="C1687")
print(stress_shift_3dict)
print(nrow(stress_shift_3dict))
```

### Task B

```{r}
stress_shift_3dict_using_pipe <- d %>% dplyr::filter(Dict=="W1802"|Dict=="J1917"|Dict=="C1687") %>% print
identical(stress_shift_3dict,stress_shift_3dict_using_pipe)
```

### Task C

```{r}
stress_shift_3dict_nouns <- dplyr::filter(stress_shift_3dict,Category=="Noun")
stress_shift_3dict_verbs <- dplyr::filter(stress_shift_3dict,Category=="Verb")
stress_shift_3dict_using_bind <- dplyr::bind_rows(stress_shift_3dict_nouns,stress_shift_3dict_verbs)
stress_shift_3dict_using_bind_reversed <- dplyr::bind_rows(stress_shift_3dict_verbs,stress_shift_3dict_nouns)
print(stress_shift_3dict_using_bind)
print(stress_shift_3dict_using_bind_reversed)
identical(stress_shift_3dict,stress_shift_3dict_using_bind)
identical(stress_shift_3dict,stress_shift_3dict_using_bind_reversed)
```

The identical one is identical to the original data even in term of the data order and the other not, so it's not identical. I think this maybe influences when I have permuted data, but I have some doubt that if I permute it for thousand times, what it will give me.

### Task D

```{r}
d_nouns <- dplyr::filter(d,Category=="Noun")
stress_shift_nouns <- dplyr::select(d_nouns,Word,Dict,Syllable)
stress_shift_nouns_renamed <- dplyr::rename(stress_shift_nouns,Syllable_Noun=Syllable)

# way 2, imitation of the Task B
stress_shift_nouns_renamed_try <- d %>% dplyr::filter(Category=="Noun") %>%
            dplyr::select(Word,Dict,Syllable) %>%
            dplyr::rename(Syllable_Noun=Syllable)
            
print(stress_shift_nouns_renamed)
# print(stress_shift_nouns_renamed_try)
identical(stress_shift_nouns_renamed_try,stress_shift_nouns_renamed)

stress_shift_verbs_renamed <- d %>% dplyr::filter(Category=="Verb") %>%
                            dplyr::select(Word,Dict,Syllable) %>%
                            dplyr::rename(Syllable_Verb=Syllable)

stress_shift_wide <- dplyr::inner_join(stress_shift_nouns_renamed,stress_shift_verbs_renamed)
print(stress_shift_wide)
```

The `stress_shift_wide` looks at all the words from all the dictionaries and compare the syllable strengthen when they are nouns and verbs. Some words are only Noun and some words are only Verb, so if we look at the words who have two possible syllable strengthen, then there must be some loss.

### Task E

```{r}
ggplot2::ggplot(stressshift::stress_shift_unamb,
                ggplot2::aes(x=Category, fill=Syllable)) +
  ggplot2::geom_bar(position="dodge", colour="black") + 
  ggplot2::scale_fill_brewer(palette="Set3")
```

### Task F

```{r}
stress_shift_byword <- 
  stress_shift_wide %>% 
  dplyr::group_by(Word) %>%
  dplyr::summarise(
    Noun_Percent_Syll_1=length(Syllable_Noun[Syllable_Noun=="Syllable 1"])/n(),
    Verb_Percent_Syll_1=length(Syllable_Verb[Syllable_Verb=="Syllable 1"])/n())

print(stress_shift_byword)
print(nrow(stress_shift_byword))
```

### Task G

```{r}
p <- ggplot2::ggplot(stress_shift_byword,ggplot2::aes_string(x="Noun_Percent_Syll_1",y="Verb_Percent_Syll_1")) +
  ggplot2::geom_point(mapping=NULL)
print(p)
```

### Task H

```{r}
stress_shift_byword_all <- 
  dplyr::group_by(stressshift::stress_shift_unamb,Word) %>%
  dplyr::summarise(
    Noun_Percent_Syll_1 = length(Syllable[Syllable=="Syllable 1"&Category=="Noun"])/length(Syllable[Category=="Noun"]),
    Verb_Percent_Syll_1 = length(Syllable[Syllable=="Syllable 1"&Category=="Verb"])/length(Syllable[Category=="Verb"]))
print(stress_shift_byword_all)
```

```{r}
dpfilter <- dplyr::filter
ggplot <- ggplot2::ggplot
```

## Exercise 2

### Task B

```{r}
print(difference_in_proportion(stressshift::stress_shift_unamb,"Syllable", "Category", "Noun","Verb","Syllable 1")) # TRÈS IMPORTANT !!! CATEGORY should with "", otherwise OBJET INTROUVABLE
```

### Task B

```{r}
if(!exists(".Random.seed")) set.seed(NULL)
previous_seed <- .Random.seed
set.seed(1)
ptest_stress <- permutation_twogroups(stressshift::stress_shift_unamb,
                      "Syllable", "Category", "Noun", "Verb",
                      difference_in_proportion,
                      n_samples=99,
                      "Syllable 1")
set.seed(previous_seed)
permutation_pvalue_right(ptest_stress)
ptest_stress
```

```{r}
ptest_stress_permuted <- tibble::as_tibble(ptest_stress["permuted"])
ptest_stress_observe <- as.numeric(ptest_stress["observed"])
p <- ggplot(ptest_stress_permuted,
            ggplot2::aes_string(x="permuted",y="..count.."))+ # define the x and y
  ggplot2::geom_histogram(colour="skyblue",fill="skyblue",binwidth = 0.005)+ # tell R clearly that the object is a histogram
   ggplot2::geom_vline(ggplot2::aes(xintercept=ptest_stress_observe), lwd=0.5, color="skyblue")
print(p)
```

## Exercise 3

### Task A

```{r}
n_n <- sum(stressshift::stress_shift_unamb$Category=="Noun")
n_v <- sum(stressshift::stress_shift_unamb$Category=="Verb")
n_sy_n <- sum(stressshift::stress_shift_unamb$Category=="Noun" & stressshift::stress_shift_unamb$Syllable=="Syllable 1")
n_sy_v <- sum(stressshift::stress_shift_unamb$Category=="Verb" & stressshift::stress_shift_unamb$Syllable=="Syllable 1")
prop_n <- n_sy_n/n_n
prop_v <- n_sy_v/n_v
print(n_n)
print(n_v)
print(prop_n)
print(prop_v)
```

```{r}
simulate_n <- rbinom(1000, n_n, prop_n)
simulate_v <- rbinom(1000, n_v, prop_v)

Replication <- paste0("R", sprintf("%04d", 1:1000))
Noun_N_Syll_1 <- c(simulate_n)
Verb_N_Syll_1 <- c(simulate_v)
Noun_Percent_Syll_1 <- stress_shift_replications$Noun_N_Syll_1/n_n
Verb_Percent_Syll_1 <- stress_shift_replications$Verb_N_Syll_1/n_v
Difference_in_Proportion <- stress_shift_replications$Noun_Percent_Syll_1-stress_shift_replications$Verb_Percent_Syll_1

stress_shift_replications <- data.frame(Replication,Noun_N_Syll_1,Verb_N_Syll_1,Noun_Percent_Syll_1,Verb_Percent_Syll_1,Difference_in_Proportion)

print(stress_shift_replications)
```

```{r}

ptest_stress_observe <- as.numeric(ptest_stress["observed"])
p_rep <- ggplot(stress_shift_replications,
            ggplot2::aes_string(x="Difference_in_Proportion",y="..count.."))+ # define the x and y
  ggplot2::geom_histogram(colour="skyblue",fill="skyblue",binwidth = 0.005)+ # tell R clearly that the object is a histogram
   ggplot2::geom_vline(ggplot2::aes(xintercept=ptest_stress_observe), lwd=0.5, color="skyblue")+
  ggplot2::xlim(c(-0.1, 0.8))
print(p_rep)
```

```{r}
ptest_stress_permuted <- tibble::as_tibble(ptest_stress["permuted"])
ptest_stress_observe <- as.numeric(ptest_stress["observed"])
p <- ggplot(ptest_stress_permuted,
            ggplot2::aes_string(x="permuted",y="..count.."))+ # define the x and y
  ggplot2::geom_histogram(colour="skyblue",fill="skyblue",binwidth = 0.005)+ # tell R clearly that the object is a histogram
   ggplot2::geom_vline(ggplot2::aes(xintercept=ptest_stress_observe), lwd=0.5, color="skyblue")+
  ggplot2::xlim(c(-0.1, 0.8))
print(p)
```

Because the new "stress_shift_replications" one is simulated by obeying the exact probability of "proportion of Syllable 1 in Nouns" and "in Verbs", however the permuted one is permuted by randomly disturbing all the data. So there's necessarily a big difference between them.

```{r cache=TRUE}
stress_shift_replications <- stress_shift_replications %>%
  dplyr::mutate(
    Permutation_Pvalue = v_pdp_pvalue_right(Noun_N_Syll_1, Verb_N_Syll_1,
                                            n_n,
                                            n_v,
                                            n_samples=99))
print(stress_shift_replications)
```

- with one tenth the number of observations in each group (651 noun and 673 verb observations)

```{r}
simulate_n <- c(rbinom(100, n_n, prop_n))
simulate_v <- c(rbinom(100, n_v, prop_v))
stress_shift_replications_onetenth <- stress_shift_replications %>%
  dplyr::mutate(
    Permutation_Pvalue = v_pdp_pvalue_right(simulate_n, simulate_v,
                                            651,
                                            673,
                                            n_samples=9))
print(stress_shift_replications_onetenth)
```

- with the same overall number of observations, but with one tenth as many observations for verbs as for nouns (12034 noun and 1204 verb observations)

```{r}
stress_shift_replications_tennouns <- stress_shift_replications %>%
  dplyr::mutate(
    Permutation_Pvalue = v_pdp_pvalue_right(Noun_N_Syll_1, Verb_N_Syll_1,
                                            12034,
                                            1204,
                                            n_samples=99))
print(stress_shift_replications_tennouns)
```

- with a total of only 33 observations (16 noun observations and 17 verb observations)

```{r}
stress_shift_replications_tennouns <- stress_shift_replications %>%
  dplyr::mutate(
    Permutation_Pvalue = v_pdp_pvalue_right(Noun_N_Syll_1, Verb_N_Syll_1,
                                            12034,
                                            1204,
                                            n_samples=99))
print(stress_shift_replications_tennouns)
```

